---
title: "Data Science mit R"
author: "Iskender Dilaver"
date: "2024-05-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Download package ggplot2

```{r}
if (!require(ggplot2)) {
  install.packages("ggplot2")
}
library(ggplot2)
```


# Import the data("iris")

```{r}
data(iris)
head(iris)
summary(iris)
```

# Make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  labs(title = "Scatter Plot of Sepal Length and Width by pecies",
       x = "Sepal Length",
       y = "Sepal Width") 
```

# Add Regression Line

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Scatter Plot of Sepal Length and Width by Species with regression line",
       x = "Sepal Length",
       y = "Sepal Width") 
```

# Calculate the Pearson correlation for this plot

```{r}
correlation <- cor(iris$Sepal.Length, iris$Sepal.Width)
correlation

```


# Make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
ggplot(iris, aes(x = Species, y = Petal.Width, fill = Species)) +
  geom_boxplot() +
  labs(title = "Boxplot of Petal Width by Species",
       x = "Species",
       y = "Petal Width")
```


# Make the histogram for Petal.Width with 3 species separately in x-axis in different colors
```{r}
ggplot(iris, aes(x = Petal.Width, fill = Species)) +
  geom_histogram(binwidth = 0.1, position = "dodge") +
  labs(title = "Histogram of Petal Width by Species",
       x = "Petal Width",
       y = "Count")
```

# Run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

```{r}
setosa_petal_width <- subset(iris, Species == "setosa")$Petal.Width
virginica_petal_width <- subset(iris, Species == "virginica")$Petal.Width

t_test_result <- t.test(setosa_petal_width, virginica_petal_width)
t_test_result

# Conclusion
if (t_test_result$p.value < 0.05) {
  conclusion <- "There is a statistically significant difference in Petal Width between Setosa and Virginica."
} else {
  conclusion <- "There is no statistically significant difference in Petal Width between Setosa and Virginica."
}
conclusion
```